---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Myappkg

A package about reproducible shiny of figure 3 in "COVID-19 in low-tolerance border quarantine systems: Impact of the Delta variant of SARS-CoV-2"，(Zachreson et al., 2022). The outcome is a reproducible  multi-layered heat map. Under the same quarantine system, the community infection pressure(in the article  the authors aggregate the infectivity of all leaks in the community into a single indicator, $\beta$_tot) due to breach events relative size relative to a "baseline case", and how they will change with two things VE and R0

The goal of myappkg is to get heap maps under specific range of R0 (virus spead capability) and VE (vaccine efficiency).

## Installation

You can install the development version of myappkg from [GitHub](ETC5523-2025/assignment-4-packages-and-shiny-apps-shaocaoyu-01) with:

``` {r}
# install.packages("pak")
remotes::install_github("ETC5523-2025/assignment-4-packages-and-shiny-apps-shaocaoyu-01")
```

## Usage Examples
The following steps demonstrates how to use this to get a fresh heatmap.
1. Open the inst/app/app.R
2. Click on the Run button 


## Developing
In addition to providing the heat map, myappkg also provide the contour of the $\beta$_tot, the line chart of the $\beta$_tot vs VE by R0 and the line chart of the $\beta$_tot vs R0 by VE. Besides, it provides the raw data download and preview functions.  

## Data citation
Zachreson, C., Shearer, F. M., Price, D. J., Lydeamore, M. J., McVernon, J., McCaw, J., & Geard, N. (2022). COVID-19 in low-tolerance border quarantine systems: Impact of the Delta variant of SARS-CoV-2. Science Advances, 8, eabm3624. https://doi.org/10.1126/sciadv.abm3624

## Reference
Zachreson, C., Shearer, F. M., Price, D. J., Lydeamore, M. J., McVernon, J., McCaw, J., & Geard, N. (2022). COVID-19 in low-tolerance border quarantine systems: Impact of the Delta variant of SARS-CoV-2. Science Advances, 8, eabm3624. https://doi.org/10.1126/sciadv.abm3624



