---
title: "getting-started with myappkg"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{getting-started with myappkg}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Overview
Myappkg provide the reproducible shiny of figure 3 in "COVID-19 in low-tolerance border quarantine systems: Impact of the Delta variant of SARS-CoV-2"，(Zachreson et al., 2022). Myappkg also provide the contour of the $\beta$_tot, the line chart of the $\beta$_tot vs VE by R0 and the line chart of the $\beta$_tot vs R0 by VE. Besides, it provides the raw data download and preview functions.


## Install & Load
```{r setup}
library(myappkg)
```

## Included Data
The data is from the journal "COVID-19 in low-tolerance border quarantine systems: Impact of the Delta variant of SARS-CoV-2"，(Zachreson et al., 2022). It is about the $\beta$_tot value to the different range of R0 and VE.

